---
title: "Short Word Report - Model Comparison"
output: 
  word_document: 
    fig_caption: yes
params:
  Stock: NA
  Species: NA
  Abundance: NA
  FCYear: NA  
  Table_Multi_Pt_FC: NA
  Table_Multi_Int_FC: NA
  Int_Type: NA
  Table_BestModels: NA
  Table_CumulRanks: NA
  Table_RetroPM: NA
  Table_RetroRanks: NA
  multifit.out: NA
  plot.sort: NA
  Plot_Values: NA
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE)
```


# Executive Summary


This document contains `r dim(params$multifit.out[["table.ptfc"]])[1]` alternative `r params$FCYear` forecasts of `r params$Abundance` for `r params$Stock` `r params$Species`.



```{r echo = FALSE, results = "asis"}


caption.use <- paste0("Table 1:", params$FCYear, " Forecast of ",params$Abundance, " for ",params$Stock," ",params$Species,". Each row shows age-specific estimates for one of the alternative models. AvgRank is the rank of that model across age classes"    )

kable(params$Table_Multi_Pt_FC, 
		caption = caption.use,
		format = "pandoc")
```





```{r echo = FALSE, results = "asis"}


caption.use <- paste0("Table 2:", params$FCYear, " Forecast of ",params$Abundance, " for ",params$Stock," ",params$Species,". Rows shows forecasts for highest-ranked models by age and alternative total forecasts."    )

kable(params$Table_BestModels, 
		caption = caption.use,
		format = "pandoc")
```



\newpage

# Forecast Distribution Plots

This section has a series of plots, one for each age class and the total forecast. Each panel shows the point forecast (point),  as well as the median (*X*) and upper/lower bounds of the `r toupper(params$Int_Type)` distribution. Models are labelled with the user-specified name, followed by the model rank in brackets. Models can be arranged either by rank or by increasing point forecast. This selection is done in the app.(Note: plots are generated in a *for* loop, and we haven't figured out how to do captions for each plot. But it's on the to do list...)



```{r echo = FALSE, results = "asis",fig.cap = "\\label{fig:figs}plotting example"}


table.allages <-	params$Plot_Values
		
age.classes <- unique(table.allages$Age)
		
for(age.plot in age.classes){
					
				table.use <-  table.allages %>% dplyr::filter(Age == age.plot) %>% select(-Age)


     			if(params$plot.sort == "AvgRank") {table.use <-  table.use %>% arrange(RankByAge)}
     			if(params$plot.sort == "Forecast") {table.use <-  table.use %>% arrange(PtFC)}

         			n.models <- dim(table.use)[1]
					vec.plot <- table.use$PtFC
					fc.p50 <- table.use$p50
					fc.p10 <- table.use$p10
					fc.p90 <- table.use$p90

					par(mai=c(0.8,1.8,0.4,0))

					plot(vec.plot , n.models:1, axes=FALSE,xlim = c(0,max(fc.p90)), xlab="Forecast",ylab="", ylim=c(0,n.models+1),
							pch=19,type="p",cex=1.1,col="red",cex.lab=0.9,main=age.plot,col.main="darkblue")
					abline(h=1:n.models,col="lightgrey")
					segments(fc.p10,n.models:1,fc.p90, n.models:1,col="red",lwd=2)

					# Pt FC
					points(vec.plot , n.models:1, pch=19,type="p",cex=1.5,col="red")
					text(vec.plot , (n.models:1)+0.3, labels=prettyNum(round(vec.plot),big.mark=","),cex=0.8,col="red")



					# bounds labels
					points(fc.p50 , n.models:1, pch=4,type="p",cex=1.5,col="red")
					text(fc.p10 , (n.models:1)+0.2, labels=prettyNum(round(fc.p10),big.mark=","),cex=0.7,col="red")
					text(fc.p90 , (n.models:1)+0.2, labels=prettyNum(round(fc.p90),big.mark=","),cex=0.7,col="red")


					axis(2,at=n.models:1,labels=paste0(table.use$Model," (",table.use$RankByAge,")"),las=2,cex.axis=0.8)
					axis(1,cex.axis=0.8)
					
					
					}
					
					
	
					

```


